### 2011-10-31 doc/theses/vitasek/chapter-3-mip.tex
Thesis: in progress.

\section{Finding ID Sets With GLPK}

@@

\subsection{Constructions Heuristics}
\label{section-mip-chs}
% TODO can I format things in nomenclature?
\nomenclature{CH}{Construction Heuristic}

@@

The number of AMs to remove from each solution is specified as ratio from $(0, 1)$ of the solution size (number of AMs in solution). For example, \heu{Random Remove} with $ratio = 0.1$ would remove 1 random AM from a solution containing 10 AMs and 2 from a solution containing 17 AMs (due to rounding).

@@

\begin{algorithm}
\caption{\heu{Random Remove} IH}
\label{listing-ih-randomremove}
\begin{algorithmic}
\REQUIRE $FP$ pool of feasible solutions
\REQUIRE $k \in (0,1)$ ratio of AMs to remove from each $s \in FP$
\ENSURE pool of feasible solutions
\FORALL{$s \in FP$}
  \STATE $K \gets k * |s|$
  \STATE remove $K$ random AMs from $s$
\ENDFOR
\RETURN $FP$
\end{algorithmic}
\end{algorithm}

@@

This simple improvement heuristic assumes that the solutions in the pool are not ``complete", i.e. there are AMs that could be added to them without violating the ID set condition.

>>>>

\section{Finding ID Sets With GLPK}
\label{section-mip-glpk}

@@

\subsection{Constructions Heuristics}
\label{section-mip-chs}
\nomenclature{CH}{Construction Heuristic}

@@

The number of AMs to remove from each solution is specified as fraction from $(0, 1)$ of the solution size (number of AMs in solution). For example, \heu{Random Remove} with $fraction = 0.1$ would remove 1 random AM from a solution containing 10 AMs and 2 from a solution containing 17 AMs (due to rounding).

@@

\begin{algorithm}
\caption{\heu{Random Remove} IH}
\label{listing-ih-randomremove}
\begin{algorithmic}
\REQUIRE $FP$ pool of feasible solutions
\REQUIRE $k \in (0,1)$ fraction of AMs to remove from each $s \in FP$
\ENSURE pool of feasible solutions
\FORALL{$s \in FP$}
  \STATE $K \gets k * |s|$
  \STATE remove $K$ random AMs from $s$
\ENDFOR
\RETURN $FP$
\end{algorithmic}
\end{algorithm}

@@

This simple improvement heuristic assumes that the solutions in the pool are not ``complete'', i.e. there are AMs that could be added to them without violating the ID set condition.
